---
title: "Assignment 5 Task 1"
author: "Ian Brunjes"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(here)
```
```{r}
# Read in data
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r}
# Plot data
ggplot(data = ces, aes(x=white_percent, y=ces_3_0_score)) +
  geom_hex() +
  labs(
    x = "Percent Population White",
    y = "CalEnviroScreen Score",
    title = "White Population Demographic vs CalEnviroScreen Score"
  ) +
  scale_fill_gradient(low = "navy", high = "orange")+
  theme_minimal()
```

## Description of Graph:
The above graph displays how the CalEnvrioScreen Score, a measure of pollution burdens and vulnerable population characteristics, changes inversely with the amount of a population identifying as white. This is a graphical representation of the environmental injustices frequently faced by minority communities after years of poor land-use planning and disinvestment. 

